Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-15 report/report.tex
Update todo
Mention SLU dataset in abstract and introduction

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by examining how common it is that these footpaths collide with other map features.
In the collision detection process, the margin of error has been taken as the positional error in the OSM dataset, which has been obtained by comparing OSM data to a dataset with a known accuracy.

@@

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM dataset and a reference dataset.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for an implementation overview, 3.2 for a walkthrough of the program implementation, and 4.1.2 for the results.

@@

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet)
\footnote{Lantmäteriet. Produktbeskrivning: GSD-Fastighetskartan vektor - Lantmäteriet. Acessed 16-04-2020. https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.
The data is collected by geodetic professionals, by using land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.

@@

% After Chris approves
% TODO: Spell check
% TODO: Swedish abstract

>>>>

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by examining how common it is that these footpaths collide with other map features.
In the collision detection process, the margin of error has been taken as the positional error in the OSM dataset, which has been obtained by comparing OSM data to the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy.

@@

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM building dataset and the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for an implementation overview, 3.2 for a walkthrough of the program implementation, and 4.1.2 for the results.

@@

The SLU map is maintained and published by The Swedish National Land Survey (Swedish: Lantmäteriet)
\footnote{Lantmäteriet. Produktbeskrivning: GSD-Fastighetskartan vektor - Lantmäteriet. Acessed 16-04-2020. https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}.
The data is collected by geodetic professionals, by using land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.

@@

% NOW-NOW:
% TODO: Make clear that a footpath is a type of road. Even sidewalks that run along main roads are classified as roads in OSM.
% TODO: Abstract: Reduce first paragraph (background)
% TODO: Use overlap instead of collision outside of technical contexts

% NOW:
% TODO: Introduce concepts: Collision, overlap, error
% TODO: Come up with a sentence that explains why errors could cause overlap. Repeat it in Introduction, research question and the abstract
% TODO: The word footpath does not appear anywhere in the TOC
% TODO: Abstract: Provide more detail about what was done and how it was evaluated - rephrase "In the collision detection process"

% LATER:
% TODO: Image with road collision (Accurate data vs inaccurate data)
% TODO: Swedish abstract

% After Chris approves
% TODO: New thesis name
% TODO: Spell check
